HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-04-28 docs/HLL_exp_bad/main.tex
rect adv mod in exp sec

To assess the efficiency of our attacks, we can compare our results from Table~\ref{table:tab2} with the attack presented in Section 5.1 of~\cite{hllvuln}. In that paper, the authors target the Redis~\cite{redis} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250,000 items, the adversary could choose ``74,390 distinct items and obtain an HLL estimate of only 15,780``~\cite{hllvuln}, achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125,000 distinct items while keeping the cardinality estimate at 367, providing a reduction by a factor of 340 instead of 5. \kenny{I think we can say more here -- isn't it true that the attack in Section 5.1 of~\cite{hllvuln} is in the M2 scenario? Which is our S1? Whereas the attack you describe here is more like an S2 attack, a much weaker attack model?}

>>>>

To assess the efficiency of our attacks, we can compare our results from Table~\ref{table:tab2} with the attack presented in Section 5.1 of~\cite{hllvuln}. In that paper, the authors target the Redis~\cite{redis} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250,000 items, the adversary could choose ``74,390 distinct items and obtain an HLL estimate of only 15,780``~\cite{hllvuln}, achieving a five-fold reduction from the true cardinality. The authors present this setup as the M2 scenario, without providing any explanation. When looking at the open-source code, we could gain details on the implementation that any attacker could obtain, and thus argue that based on this knowledge, the adversarial scenario is actually M1 (S2 in this work), making the comparison relevant. In comparison, the adversary following our strategy is able to add 125,000 distinct items while keeping the cardinality estimate at 367, providing a reduction by a factor of 340 instead of 5.
